Predictive Regressions with Persistent Regressors:\\ Monte Carlo evidence for the Bonferroni Q-test

### 2019-09-12 paper.tex
ADD bib

\documentclass{article}
\usepackage{amsmath}
\usepackage{mathrsfs}  
\usepackage{float}
\usepackage{varioref}
\usepackage[margin=1.2in]{geometry}
\usepackage[flushleft]{threeparttable}
\title{Predictive Regressions with Persistent Regressors}
\author{Jan Philipp Wöltjen  \\
	Seminar in Statistics CAU Kiel  \\
	}

@@

\section{Derivation of the tests}
\label{Derivation of the tests}
\subsection{Infeasible tests}
\label{Infeasible tests}
In developing their test, Campbell and Yogo (2006) start by considering the t-statistic 
\begin{equation}
t\left(\beta_{0}\right)=\frac{\widehat{\beta}-\beta_{0}}{\sigma_{u}\left(\sum_{t=1}^{T} x_{t-1}^{\mu 2}\right)^{-1 / 2}},
\end{equation}
where $x_{t-1}^{\mu}=x_{t-1}-T^{-1} \sum_{t=1}^{T} x_{t-1}$ denotes the de-meaned regressor and $\widehat{\beta}$ is the OLS estimate of $\beta$. They argue that this test ignores information contained in the system ($\ref{eqn:1}$, $\ref{eqn:2}$) and can thus not be optimal. To see this, consider the joint log likelihood function of the system ($\ref{eqn:1}$, $\ref{eqn:2}$)
\begin{equation}
\begin{aligned} L(\beta, \rho, \alpha, \gamma)=&-\frac{1}{1-\delta^{2}} \sum_{t=1}^{T}\left[\frac{\left(r_{t}-\alpha-\beta x_{t-1}\right)^{2}}{\sigma_{u}^{2}}-2 \delta \frac{\left(r_{t}-\alpha-\beta x_{t-1}\right)\left(x_{t}-\gamma-\rho x_{t-1}\right)}{\sigma_{u} \sigma_{e}}\right.\\ &\left.+\frac{\left(x_{t}-\gamma-\rho x_{t-1}\right)^{2}}{\sigma_{e}^{2}}\right] \end{aligned}
\end{equation}
and observe that the t-test squared is equal to the likelihood ratio test statistic
\begin{equation}
\max _{\beta, \rho, \alpha, \gamma} L(\beta, \rho, \alpha, \gamma)-\max _{\rho, \alpha, \gamma} L\left(\beta_{0}, \rho, \alpha, \gamma\right)=t\left(\beta_{0}\right)^{2}.
\end{equation}
But this test statistic turns out to be the same if only the marginal log likelihood 
\begin{equation}
L(\beta, \alpha)=-\sum_{t=1}^{T}\left(r_{t}-\alpha-\beta x_{t-1}\right)^{2}
\end{equation}
is used in its computation. Thus the t-test ignores information about $\rho$.

@@

\section{Monte Carlo simulation}
This section accommodates, next to the out-of-sample results in section $\ref{Empirical Results}$, one of the main contributions of this study. First, Monte Carlo evidence of Campbell and Yogo (2006) is replicated providing reassurance that both parties implemented the method correctly. Next, the Bonferroni Q-test is tested by violating key assumptions about the regressor's persistence. Furthermore, innovations are modeled by increasingly realistic distributions, for which justification in form of real-world parameter estimates is given.
\label{Monte Carlo simulation}
\subsection{Simulation with Gaussian innovations}
\label{Simulation with Gaussian innovations}
To confirm the correct implementation of the procedure, Table~\vref{tab:cy} replicates Table 3 of Campbell and Yogo (2006) with the same input parameters. For each parameter combination, 10,000 Monte Carlo samples are drawn from a multivariate standard normal distribution with correlation $\delta$. These variates represent the innovations, which are used to simulate sample paths according to system ($\ref{eqn:1}$, $\ref{eqn:2}$). The null hypothesis $H_0: \beta = 0$ is tested against the alternative $H_1: \beta > 0$ at the 5\% significance level. If the Bonferroni confidence interval lies strictly above zero, the one-sided test is rejected. 
\begin{table}[hb!]
\caption{Finite-sample rejection rates}
\label{tab:cy}
\centering

@@

As argued by Phillips (2014), the feasible Q-test as derived in section $\ref{Derivation of the tests}$ is asymptotically invalid when the largest autoregressive root of the regressor is not local-to-unity. In the following, finite-sample behavior is demonstrate as $\rho$ diverges from unity. Again, 10,000 Monte Carlo simulations are run with bivariate Gaussian innovations. A relatively small sample size is chosen to keep the DF-GLS statistic small in absolute value and thus stay in the vicinity of the implementation of Campbell and Yogo (2005). Table~\vref{tab:non-local} shows that as $\rho$ distances itself from the unity neighborhood the Bonferroni Q-test significantly over-rejects the true null of no predictability. Over-rejection is largest for highly correlated innovations and large $|c|$ where it surpasses 200\%.

@@

Campbell and Yogo (2006) evaluate the robustness of the Q-test under a fat-tailed distribution. In particular, they find finite-sample rejection probabilities to be unchanged from the Gaussian case when the innovations follow a Student t-distribution with five degrees of freedom. As shown by Cavaliere (2004), unit root tests may be invalid under conditional heteroskedasticity. Assumptions in form of equation ($\ref{eqn:covarst}$) imply validity of the Q-test under conditionally heteroskedastic innovations only if they are covariance stationary. 

@@

\begin{table}[hbt]
\centering
\caption{Finite-sample rejection rates (common stochastic trend GJR-GARCH)}
\label{tab:mc_grj-garch}
\begin{threeparttable}
\begin{tabular}{rrrrrrrrrr}
  \hline
  & Obs & $c$ & $\rho$ & $\delta$ & $\alpha_{_{GARCH}}$ & $\beta_{_{GARCH}}$ & t-test &BQ& BQ$_{{2sided}}$ \\ 
  \hline
1 & 50 & -2 & 0.961 & -0.9500 & 0.0000 & 0.95 & 0.2836 & 0.1001 & 0.1033 \\ 
  2 & 50 & -2 & 0.961 & -0.9500 & 0.0000 & 0.90 & 0.2736 & 0.0946 & 0.0986 \\ 
  3 & 50 & -2 & 0.961 & -0.9500 & 0.0000 & 0.80 & 0.2635 & 0.0952 & 0.0993 \\ 
  4 & 100 & -2 & 0.980 & -0.9500 & 0.0000 & 0.95 & 0.3054 & 0.0757 & 0.0802 \\ 
  5 & 100 & -2 & 0.980 & -0.9500 & 0.0000 & 0.90 & 0.2811 & 0.0662 & 0.0727 \\ 
  6 & 100 & -2 & 0.980 & -0.9500 & 0.0000 & 0.80 & 0.2801 & 0.0685 & 0.0734 \\ 
   \hline
\end{tabular}
 \begin{tablenotes}
 \small
\item This Table displays the finite-sample rejection rates of the true null for right-tailed [BQ] and two-tailed  [BQ$_{{2sided}}$] Bonferroni Q-tests of predictability at $\alpha$=0.05 and $\alpha$=0.1, respectively, with the variances of innovations sharing a common stochastic trend which is modeled as a univariate GJR-GARCH(1, 1) process. 10,000 Monte Carlo simulations are performed.
\end{tablenotes}
\end{threeparttable}
\end{table}

@@

\begin{table}[hb]

@@

For all datasets, both regressors are highly negatively correlated with returns. The confidence interval for $\rho$ is very near to unity in all cases, and containing it in some. Hence, the pretest of section $\ref{pretest}$ indicates non-standard null distribution of the t-test for every sampling frequency and regressor, invalidating inference based on t-statistics, which otherwise would be statistically significant. Based on the Bonferroni Q-test, the null hypothesis of no predictability can be rejected at the 5\% significance level for ldp and lep at the annual sampling frequency and for all datasets, respectively, using data from Campbell and Yogo (2006). 

@@

\begin{table}[h]

@@

Since the original publication of Campbell and Yogo (2006) a sufficiently large amount of data has been generated at the quarterly and monthly sampling frequencies that merits a standalone out-of-sample analysis. Table~\vref{tab:oos} displays model parameter estimates since 2004 until the last available data point in 2017. This relatively small dataset allows no rejection of the null hypothesis at the 5\% significance level for any of the regressors and sampling frequencies considered. Both regressors are still highly persistent at all sampling frequencies, demonstrated by the confidence interval for $\rho$ containing unity in all cases. 
\begin{table}[h]
\small
\setlength\tabcolsep{5.3pt}
\centering
\caption{Out-of-sample estimates of model parameters}
\label{tab:oos}
\begin{threeparttable}
\begin{tabular}{llrrlrrrrrl}
  \hline
dataset & $x$ & obs & $\hat{\delta}$ & $CI_{\rho}$ & DF-GLS & $p$ &t-stat & pt & $\hat{\beta}$ & $CI_{\beta}$ \\ 
  \hline
  %CRSP\_A  & lep & 14 & -0.97 & [0.036,0.97] & -1.821 & 1 & 1.81 & 0 & 0.527 & [-0.055,1.07] \\ 
  %CRSP\_A  & ldp & 14 & -0.92 & [-1.468,0.015] & -3.283 & 1 & 1.63 & 0 & 0.446 & [0.319,2.044] \\ 
  %CRSP\_A  & tbl & 14 & -0.92 & [-1.468,0.015] & -3.283 & 1 & -1.47 & 1 & -3.865 & [0.319,2.044] \\ 
  %CRSP\_A  & tms & 14 & -0.01 & [0.333,0.593] & -1.791 & 1 & 0.67 & 1 & 2.630 & [-0.258,0.611] \\ 
  CRSP\_Q  & lep & 53 & -0.99 & [0.792,1.023] & -1.607 & 1 & 1.48 & 0 & 0.101 & [-0.059,0.202] \\ 
  CRSP\_Q & ldp & 53 & -0.97 & [0.778,1.001] & -1.708 & 1 & 0.86 & 0 & 0.060 & [-0.134,0.142] \\ 
 % CRSP\_Q  & tbl & 53 & -0.97 & [0.778,1.001] & -1.708 & 1 & -0.67 & 1 & -0.409 & [-0.134,0.142] \\ 
  %CRSP\_Q  & tms & 53 & 0.19 & [0.904,0.955] & -1.335 & 1 & -0.29 & 1 & -0.248 & [-0.1,0.077] \\ 
  CRSP\_M & lep & 168 & -0.99 & [0.955,1.014] & -1.211 & 1 & 1.02 & 0 & 0.020 & [-0.025,0.041] \\ 
  CRSP\_M & ldp & 168 & -0.98 & [0.961,1.012] & -1.091 & 1 & 0.59 & 0 & 0.012 & [-0.052,0.012] \\ 
  %CRSP\_M & tbl & 168 & 0.21 & [0.991,1.001] & -0.619 & 1 & -0.66 & 1 & -0.120 & [-0.016,0.006] \\ 
  %CRSP\_M & tms & 168 & 0.10 & [0.991,1.001] & -0.565 & 1 & -0.58 & 1 & -0.142 & [-0.035,0.02] \\ 
\hline
\end{tabular}
 \begin{tablenotes}
 \small
\item Data is taken from Amit Goyal’s Website. Stock returns are the SP 500 index log-returns from 2004 to 2017 from the Center for Research in Security Press (CRSP) minus the rolled over 3-month T-bill rate. lep is the log 10 year moving average earnings/price ratio (2004 to 2017). ldp is the log dividend/price ratio (2004 to 2017).
% tbl is the 3-month T-bill rate (1952 to 2017). tms is the term-spread between long-term government bonds and tbl (1952 to 2017). 
$p$ denotes the optimal number of lags selected by BIC. pt is a boolean denoting whether the pretest of section $\ref{pretest}$ rejects the null of actual size greater than 0.075. $CI_{\rho}$ and $CI_{\beta}$ denote the confidence interval for $\rho$ and $\beta$, respectively.
\end{tablenotes}
\end{threeparttable}
\end{table}

>>>>

\documentclass{article}
\usepackage{amsmath}
\usepackage{mathrsfs}  
\usepackage{float}
\usepackage{varioref}
\usepackage[margin=1.45in]{geometry}
\usepackage[flushleft]{threeparttable}
\title{Predictive Regressions with Persistent Regressors:\\ Monte Carlo evidence for the Bonferroni Q-test}
\author{Jan Philipp Wöltjen  \\
	Seminar in Statistics CAU Kiel  \\
	}

@@

\section{Derivation of the tests}
\label{Derivation of the tests}
\subsection{Infeasible tests}
\label{Infeasible tests}
In developing their test, Campbell and Yogo (2006) start by considering the t-statistic 
\begin{equation}
t\left(\beta_{0}\right)=\frac{\widehat{\beta}-\beta_{0}}{\sigma_{u}\left(\sum_{t=1}^{T} x_{t-1}^{\mu 2}\right)^{-1 / 2}},
\end{equation}
where $x_{t-1}^{\mu}=x_{t-1}-T^{-1} \sum_{t=1}^{T} x_{t-1}$ denotes the demeaned regressor and $\widehat{\beta}$ is the OLS estimate of $\beta$. They argue that this test ignores information contained in the system ($\ref{eqn:1}$, $\ref{eqn:2}$) and can thus not be optimal. To see this, consider the joint log likelihood function of the system ($\ref{eqn:1}$, $\ref{eqn:2}$)
\begin{equation}
\begin{aligned} L(\beta, \rho, \alpha, \gamma)=&-\frac{1}{1-\delta^{2}} \sum_{t=1}^{T}\left[\frac{\left(r_{t}-\alpha-\beta x_{t-1}\right)^{2}}{\sigma_{u}^{2}}-2 \delta \frac{\left(r_{t}-\alpha-\beta x_{t-1}\right)\left(x_{t}-\gamma-\rho x_{t-1}\right)}{\sigma_{u} \sigma_{e}}\right.\\ &\left.+\frac{\left(x_{t}-\gamma-\rho x_{t-1}\right)^{2}}{\sigma_{e}^{2}}\right] \end{aligned}
\end{equation}
and observe that the t-test squared is equal to the likelihood ratio test statistic
\begin{equation}
\max _{\beta, \rho, \alpha, \gamma} L(\beta, \rho, \alpha, \gamma)-\max _{\rho, \alpha, \gamma} L\left(\beta_{0}, \rho, \alpha, \gamma\right)=t\left(\beta_{0}\right)^{2}.
\end{equation}
But this test statistic turns out to be the same if only the marginal log likelihood 
\begin{equation}
L(\beta, \alpha)=-\sum_{t=1}^{T}\left(r_{t}-\alpha-\beta x_{t-1}\right)^{2}
\end{equation}
is used in its computation. Thus the t-test ignores information about $\rho$.

@@

\section{Monte Carlo simulation}
This section, next to the out-of-sample results in section $\ref{Empirical Results}$, accommodates one of the main contributions of this study. First, Monte Carlo evidence of Campbell and Yogo (2006) is replicated providing reassurance that both parties implemented the method correctly. Next, the Bonferroni Q-test is tested by violating key assumptions about the regressor's persistence. Furthermore, innovations are modeled by increasingly realistic distributions, for which justification in the form of real-world parameter estimates is given.
\label{Monte Carlo simulation}
\subsection{Simulation with Gaussian innovations}
\label{Simulation with Gaussian innovations}
To confirm the correct implementation of the procedure, Table~\vref{tab:cy} replicates Table 3 of Campbell and Yogo (2006) with the same input parameters. For each parameter combination, 10,000 Monte Carlo samples are drawn from a multivariate standard normal distribution with correlation $\delta$. These variates represent the innovations, which are used to simulate sample paths according to system ($\ref{eqn:1}$, $\ref{eqn:2}$). The null hypothesis $H_0: \beta = 0$ is tested against the alternative $H_1: \beta > 0$ at the 5\% significance level. If the Bonferroni confidence interval lies strictly above zero, the one-sided test is rejected. 
\begin{table}[hb!]
\caption{Finite-sample rejection rates}
\label{tab:cy}
\centering

@@

As argued by Phillips (2014), the feasible Q-test as derived in section $\ref{Derivation of the tests}$ is asymptotically invalid when the largest autoregressive root of the regressor is not local-to-unity. In the following, finite-sample behavior is demonstrated as $\rho$ diverges from unity. Again, 10,000 Monte Carlo simulations are run with bivariate Gaussian innovations. A relatively small sample size is chosen to keep the DF-GLS statistic small in absolute value and thus stay in the vicinity of the implementation of Campbell and Yogo (2005). Table~\vref{tab:non-local} shows that as $\rho$ distances itself from the unity neighborhood the Bonferroni Q-test significantly over-rejects the true null of no predictability. Over-rejection is largest for highly correlated innovations and large $|c|$ where it surpasses 200\%.

@@

Campbell and Yogo (2006) evaluate the robustness of the Q-test under a fat-tailed distribution. In particular, they find finite-sample rejection probabilities to be unchanged from the Gaussian case when the innovations follow a Student t-distribution with five degrees of freedom. As shown by Cavaliere (2004), unit root tests may be invalid under conditional heteroskedasticity. Assumptions in the form of equation ($\ref{eqn:covarst}$) imply validity of the Q-test under conditionally heteroskedastic innovations only if they are covariance stationary. 

@@

\begin{table}[h!]
\centering
\caption{Finite-sample rejection rates (common stochastic trend GJR-GARCH)}
\label{tab:mc_grj-garch}
\begin{threeparttable}
\begin{tabular}{rrrrrrrrrr}
  \hline
  & Obs & $c$ & $\rho$ & $\delta$ & $\alpha_{_{GARCH}}$ & $\beta_{_{GARCH}}$ & t-test &BQ& BQ$_{{2sided}}$ \\ 
  \hline
1 & 50 & -2 & 0.961 & -0.9500 & 0.0000 & 0.95 & 0.2836 & 0.1001 & 0.1033 \\ 
  2 & 50 & -2 & 0.961 & -0.9500 & 0.0000 & 0.90 & 0.2736 & 0.0946 & 0.0986 \\ 
  3 & 50 & -2 & 0.961 & -0.9500 & 0.0000 & 0.80 & 0.2635 & 0.0952 & 0.0993 \\ 
  4 & 100 & -2 & 0.980 & -0.9500 & 0.0000 & 0.95 & 0.3054 & 0.0757 & 0.0802 \\ 
  5 & 100 & -2 & 0.980 & -0.9500 & 0.0000 & 0.90 & 0.2811 & 0.0662 & 0.0727 \\ 
  6 & 100 & -2 & 0.980 & -0.9500 & 0.0000 & 0.80 & 0.2801 & 0.0685 & 0.0734 \\ 
   \hline
\end{tabular}
 \begin{tablenotes}
 \small
\item This Table displays the finite-sample rejection rates of the true null for right-tailed [BQ] and two-tailed  [BQ$_{{2sided}}$] Bonferroni Q-tests of predictability at $\alpha$=0.05 and $\alpha$=0.1, respectively, with the variances of innovations sharing a common stochastic trend which is modeled as a univariate GJR-GARCH(1, 1) process. 10,000 Monte Carlo simulations are performed.
\end{tablenotes}
\end{threeparttable}
\end{table}

@@

@@

For all datasets, both regressors are highly negatively correlated with returns. The confidence interval for $\rho$ is very near to unity in all cases, and containing it in some. Hence, the pretest of section $\ref{pretest}$ indicates non-standard null distribution of the t-test for every sampling frequency and regressor, invalidating inference based on t-statistics, which otherwise would be statistically significant. Based on the Bonferroni Q-test, the null hypothesis of no predictability can be rejected at the 5\% significance level for ldp and lep at the annual sampling frequency and for all datasets, respectively. 

@@

@@

Since the original publication of Campbell and Yogo (2006) a sufficiently large amount of data has been generated at the quarterly and monthly sampling frequencies that merits a standalone out-of-sample analysis. Table~\vref{tab:oos} displays model parameter estimates since 2004 until the last available data point in 2017. This relatively small dataset allows no rejection of the null hypothesis at the 5\% significance level for any of the regressors and sampling frequencies considered. Both regressors are still highly persistent at all sampling frequencies, demonstrated by the confidence interval for $\rho$ containing unity in all cases. 
\begin{table}[h!]
\small
\setlength\tabcolsep{5.3pt}
\centering
\caption{Out-of-sample estimates of model parameters}
\label{tab:oos}
\begin{threeparttable}
\begin{tabular}{llrrlrrrrrl}
  \hline
dataset & $x$ & obs & $\hat{\delta}$ & $CI_{\rho}$ & DF-GLS & $p$ &t-stat & pt & $\hat{\beta}$ & $CI_{\beta}$ \\ 
  \hline
  %CRSP\_A  & lep & 14 & -0.97 & [0.036,0.97] & -1.821 & 1 & 1.81 & 0 & 0.527 & [-0.055,1.07] \\ 
  %CRSP\_A  & ldp & 14 & -0.92 & [-1.468,0.015] & -3.283 & 1 & 1.63 & 0 & 0.446 & [0.319,2.044] \\ 
  %CRSP\_A  & tbl & 14 & -0.92 & [-1.468,0.015] & -3.283 & 1 & -1.47 & 1 & -3.865 & [0.319,2.044] \\ 
  %CRSP\_A  & tms & 14 & -0.01 & [0.333,0.593] & -1.791 & 1 & 0.67 & 1 & 2.630 & [-0.258,0.611] \\ 
  CRSP\_Q  & lep & 53 & -0.99 & [0.792,1.023] & -1.607 & 1 & 1.48 & 0 & 0.101 & [-0.059,0.202] \\ 
  CRSP\_Q & ldp & 53 & -0.97 & [0.778,1.001] & -1.708 & 1 & 0.86 & 0 & 0.060 & [-0.134,0.142] \\ 
 % CRSP\_Q  & tbl & 53 & -0.97 & [0.778,1.001] & -1.708 & 1 & -0.67 & 1 & -0.409 & [-0.134,0.142] \\ 
  %CRSP\_Q  & tms & 53 & 0.19 & [0.904,0.955] & -1.335 & 1 & -0.29 & 1 & -0.248 & [-0.1,0.077] \\ 
  CRSP\_M & lep & 168 & -0.99 & [0.955,1.014] & -1.211 & 1 & 1.02 & 0 & 0.020 & [-0.025,0.041] \\ 
  CRSP\_M & ldp & 168 & -0.98 & [0.961,1.012] & -1.091 & 1 & 0.59 & 0 & 0.012 & [-0.052,0.012] \\ 
  %CRSP\_M & tbl & 168 & 0.21 & [0.991,1.001] & -0.619 & 1 & -0.66 & 1 & -0.120 & [-0.016,0.006] \\ 
  %CRSP\_M & tms & 168 & 0.10 & [0.991,1.001] & -0.565 & 1 & -0.58 & 1 & -0.142 & [-0.035,0.02] \\ 
\hline
\end{tabular}
 \begin{tablenotes}
 \small
\item Data is taken from Amit Goyal’s Website. Stock returns are the SP 500 index log-returns from 2004 to 2017 from the Center for Research in Security Press (CRSP) minus the rolled over 3-month T-bill rate. lep is the log 10 year moving average earnings/price ratio (2004 to 2017). ldp is the log dividend/price ratio (2004 to 2017).
% tbl is the 3-month T-bill rate (1952 to 2017). tms is the term-spread between long-term government bonds and tbl (1952 to 2017). 
$p$ denotes the optimal number of lags selected by BIC. pt is a boolean denoting whether the pretest of section $\ref{pretest}$ rejects the null of actual size greater than 0.075. $CI_{\rho}$ and $CI_{\beta}$ denote the confidence interval for $\rho$ and $\beta$, respectively.
\end{tablenotes}
\end{threeparttable}
\end{table}
